Individual heterogeneity in the functional network topography of medial prefrontal cortex

### 2019-06-24 Manuscript.Rmd
j neuro version

**Keywords:** brain networks; DN; individual differences

@@

The community organization of PCC and mPFC was congruent with DN sub-networks A and B proposed by Braga & Buckner [-@Braga2017; @Braga2019]. The topography of our thresholded DN community closely matched network A, whereas our non-DN community included cortical territory that was not part of either DN network. Subthreshold vertices from the DN community overlaped with DN-B vertices, suggesting that this sub-network could act as a dynamic intermediary between DN-A and other networks. Our findings therefore complement the initial identification of DN sub-networks by quantifying the systematic variability of their underlying topography in a larger group of people. Understanding the interaction of networks A (DN), B, and non-DN is an important goal for future research. These two sets of results collectively suggest that canonical DN regions can be topographically partitioned into DN and non-DN communities, and that the DN community can in turn be further divided into sub-networks A and B.

@@

We thank Lauren DiNicola, Daniel Reznik, Xavier Guell, and David Somers for helpful discussions, and Daniel Sussman for initial guidance on community detection and evaluation methods. This work was supported by grants from the National Science Foundation (BCS-1755757 and BCS-1625552) and the Office of Naval Research (MURI awards N00014-16-1-2832 and N00014-17-1-2304). Data were provided by the Human Connectome Project, WU-Minn Consortium (Principal Investigators: David Van Essen and Kamil Ugurbil; 1U54MH091657) funded by the 16 NIH Institutes and Centers that support the NIH Blueprint for Neuroscience Research; and by the McDonnell Center for Systems Neuroscience at Washington University.

>>>>

## Significance Statement

  Multiple psychological functions engage topographically overlapping regions of human medial prefrontal cortex (mPFC), and the reason for the apparent overlap is not yet well understood. Here we present evidence that our understanding of the functional organization of mPFC can be advanced by accounting for individual-level topographic variability. We report results from a data-driven, network-based approach to subdividing mPFC and posterior cingulate cortex jointly into two distinct communities on the basis of non-task functional neuroimaging data. One of the identified communities corresponded to the brain's canonical default network. The community structure of mPFC was stable across test/re-test but exhibited high variability across individuals. The approach we introduce will help characterize the functional role of mPFC across diverse psychological domains.

@@

The community organization of PCC and mPFC was congruent with DN sub-networks A and B proposed by Braga & Buckner [-@Braga2017; @Braga2019]. The topography of our thresholded DN community closely matched network A, whereas our non-DN community included cortical territory that was not part of either DN network. Subthreshold vertices from the DN community overlapped with DN-B vertices, suggesting that this sub-network could act as a dynamic intermediary between DN-A and other networks. Our findings therefore complement the initial identification of DN sub-networks by quantifying the systematic variability of their underlying topography in a larger group of people. Understanding the interaction of networks A (DN), B, and non-DN is an important goal for future research. These two sets of results collectively suggest that canonical DN regions can be topographically partitioned into DN and non-DN communities, and that the DN community can in turn be further divided into sub-networks A and B.

@@

We thank Lauren DiNicola, Daniel Reznik, Xavier Guell, and David Somers for helpful discussions, and Daniel Sussman for initial guidance on community detection and evaluation methods. This work was supported by grants from the National Science Foundation (BCS-1755757 and BCS-1625552) and the Office of Naval Research (MURI award N00014-16-1-2832 and DURIP award N00014-17-1-2304). Data were provided by the Human Connectome Project, WU-Minn Consortium (Principal Investigators: David Van Essen and Kamil Ugurbil; 1U54MH091657) funded by the 16 NIH Institutes and Centers that support the NIH Blueprint for Neuroscience Research; and by the McDonnell Center for Systems Neuroscience at Washington University.
